\normalfont\spacedallcaps{Language reclamation: Literature review}

### 2023-06-18 assignment-4/article.tex
Solve 4.3

\subsection*{Exercise 4.3 (Normalizing Flows: transformation of densities)}
Problems 16.1 and 16.2 from ”Understanding Deep Learning”

>>>>

\subsection*{Exercise 4.3 (Normalizing Flows: transformation of densities)}

All problems in this section are drawn from ``Understanding Deep Learning'' \citet{prince2023understanding}.

\subsubsection*{Problem 16.1}

Consider transforming a uniform base density defined on $z\in[0,1]$ using the function $x = f[z] = z^2$. Find an expression for the transformed distribution $Pr(x)$.

\subsubsection*{Problem 16.1 solution}

Let $P_Z$ be the probability density of $z$, then $P_Z = 1$, since $z\sim U[0,1]$.

Now let $x = z^2$, then $z = \sqrt{x}$, and $\frac{dz}{dx} = \frac{1}{2\sqrt{x}}$. Let $P_X$ be the probability density of $x$. Lastly we use the change of variables formula for probability densities:

\begin{align*}
  p_X(x) &= p_Z(z) \left|\frac{dz}{dx}\right| \\
  &= 1 \cdot \left| \frac{1}{2 \sqrt{x}} \right| = \frac{1}{2\sqrt{x}}
\end{align*}
